 
To give the best feedback related to the asked questions, I write an answer for each of them. 

\paragraph*{is it reliable ?}

Yes, reliability and efficiency are the both quality TUIO team has chosen.

\paragraph*{does it have dependencies or requirements ? which ones ? if yes, could it be a problem ?}

SDL, OpenGL and GLUT libraries are required to build on Mac OS X and Linux system, but this should not create troubles.

The lack of code example and tutorial (even on web) could create difficulty in it usage.

\paragraph*{how do we build it ?}

A Microsoft Visual Studio project is given. Furthermore, a Makefile is given for Linux system. Only library dependency is needed for Mac OS X (SDL, OpenGL and GLUT).

\paragraph*{is it well coded ? what do you think ?}

Yes, classical standards of code implementation are respected, and Doxygen is in use successfully for .h files.

\paragraph*{is it scalable, configurable, tweakable ?}

Yes, according the license \textit{you can redistribute it and/or modify it under the terms of the GNU General Public License as published by the Free Software Foundation}.

\paragraph*{what are its strengths and weaknesses ?}

\subparagraph*{Strengths}

The library is offering a complete set of multi-touching interaction, which allows future evolutions if needed.

It documentation is clear and functions are self-descriptive.

An example of use is given.

Few videos and a well-noted Sourceforge repository are announcing a good library.

\subparagraph*{Weaknesses}

The library should offers to much multi-touch interaction for our requirements (to much code and documentations).

The lack of tutorials and examples could be a problem.


\paragraph*{what about the threading model, is it scalable ?}

The threading model is included into the library and should be scaled.

\paragraph*{is it worth it at the end ?}

I think this library is worth for Eiosis.
